Writing a reproducible paper with R Markdown and Pagedown^[Corresponding adress: mail@paulcbauer.eu, camille.landesvatter@mzes.uni-mannheim.de]

### 2021-06-22 paper.Rmd
Repaired table cross-references

```{r table-3, echo=TRUE, message=FALSE, warning=FALSE, results="asis"}
library(modelsummary)
library(kableExtra)
options(modelsummary_html = 'kableExtra')
datasummary_skim(mtcars, type="numeric", output="html", histogram=T) %>%
    kable_styling()
```

@@

```{r table-4, echo=TRUE, message=FALSE, warning=FALSE, results="asis"}
# Create categorical variables
mtcars$vs_cat <- as.logical(mtcars$vs)
mtcars$cyl_cat <- as.factor(mtcars$cyl)
datasummary_skim(mtcars, type="categorical", output="html")
```

@@

```{r table-5, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(modelsummary)
M1 <- lm(Fertility ~ Education + Agriculture, data = swiss)
M2 <- lm(Fertility ~ Education + Catholic, data = swiss)
M3 <- lm(Fertility ~ Education + Infant.Mortality + Agriculture, data = swiss)
models <- list("M1" = M1, "M2" =  M2, "M3" = M3)

modelsummary(models, 
         title = 'A regression table.') %>%
    kable_styling()
```

>>>>

```{r table-3, echo=TRUE}
library(modelsummary)
datasummary_skim(mtcars, 
                 type="numeric", 
                 histogram=T, 
                 title = "Summary: Numeric variables")
```

@@

```{r table-4, echo=TRUE}
# Create categorical variables
mtcars$vs_cat <- as.logical(mtcars$vs)
mtcars$cyl_cat <- as.factor(mtcars$cyl)
datasummary_skim(mtcars, 
                 type="categorical", 
                 title = "Summary: Categorical variables")
```

@@

```{r table-5, echo=TRUE}
library(modelsummary)
M1 <- lm(Fertility ~ Education + Agriculture, data = swiss)
M2 <- lm(Fertility ~ Education + Catholic, data = swiss)
M3 <- lm(Fertility ~ Education + Infant.Mortality + Agriculture, data = swiss)
models <- list("M1" = M1, "M2" =  M2, "M3" = M3)

modelsummary(models, title = 'A regression table.')
```
